Molecular Analysis

### 2023-11-06 analysis/aud_analysis.Rmd
change order of figure

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(coughs_per_min = n_coughs / TT) %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = coughs_per_min)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 93%", y_position = 6.25, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(add = c(0, .66))) +
  labs(title = "d", y = "Number of coughs per min", x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

>>>>

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(coughs_per_min = n_coughs / TT) %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = coughs_per_min)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "Posterior prob. = 93%", y_position = 6.25, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(add = c(0, .66))) +
  labs(title = "c", y = "Number of coughs per min", x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

### 2023-11-06 analysis/env_analysis.Rmd
change order of figure

```{r}
# only particle number concentration
boxpl_cn <- env_epi_data %>%
  dplyr::select(class, date, aircleaner, Cn) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = Cn)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 100%", y_position = 240, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(add = c(0, 30)), limits = c(0, NA)) +
  labs(title = "c", y = expression("Aerosol concentration (1/cm"^3*")"), x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

>>>>

```{r}
# only particle number concentration
boxpl_cn <- env_epi_data %>%
  dplyr::select(class, date, aircleaner, Cn) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = Cn)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "Posterior prob. = 100%", y_position = 240, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(add = c(0, 30)), limits = c(0, NA)) +
  labs(title = "a", y = expression("Aerosol concentration (1/cm"^3*")"), x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

### 2023-11-06 analysis/epi_analysis.Rmd
change order of figure

# number of cases by week
cases_by_cond_pl <- epi_data %>%
  group_by(aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar(stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = cases), size = 8 / cm(1), vjust = -1) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 91%", y_position = 27, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .075) +
  labs(x = "Air cleaner", y = "Number of respiratory cases", fill = "Air cleaner", title = "a") +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")

>>>>

# number of cases by week
cases_by_cond_pl <- epi_data %>%
  group_by(aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar(stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = cases), size = 8 / cm(1), vjust = -1) +
  ggsignif::geom_signif(annotations = "Posterior prob. = 91%", y_position = 27, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .075) +
  labs(x = "Air cleaner", y = "Number of respiratory cases", fill = "Air cleaner", title = "a") +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")

### 2023-11-06 analysis/mol_analysis.Rmd
change order of figure

pos_cond_pl <- df_pos_stud %>%
  ggplot(aes(x = aircleaner, y = n_pos)) +
  geom_bar(mapping = aes(fill = aircleaner), stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = n_pos), size = 8 / cm(1), vjust = -1) +
  geom_segment(data = data.frame(x = .5, xend = .5, y = 30, yend = 29), mapping = aes(x = x, xend = xend, y = y, yend = yend), color = "white") +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 65%", y_position = 30, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .1) +
  labs(x = "Air cleaner", y = "Number of positive saliva samples", title = "b") +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")

>>>>

pos_cond_pl <- df_pos_stud %>%
  ggplot(aes(x = aircleaner, y = n_pos)) +
  geom_bar(mapping = aes(fill = aircleaner), stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = n_pos), size = 8 / cm(1), vjust = -1) +
  geom_segment(data = data.frame(x = .5, xend = .5, y = 30, yend = 29), mapping = aes(x = x, xend = xend, y = y, yend = yend), color = "white") +
  ggsignif::geom_signif(annotations = "Posterior prob. = 65%", y_position = 30, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .1) +
  labs(x = "Air cleaner", y = "Number of positive saliva samples", title = "d") +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")
